Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-02-12 ms.tex
Added timing accuracy formula

\DeclareMathOperator{\cov}{cov}

@@

The \ac{CRLB} says that, element by element,
%
\begin{equation}
    \cov{
        \left(
        \begin{array}{c}
            \hat{\rho} - \rho \\
            \hat{\gamma} - \gamma \\
            \hat{\tau} - \tau
        \end{array}
        \right)
    } \geq \mathcal{I}^{-1}
\end{equation}
%
where a hat $\hat{\phantom{\rho}}$ denotes the estimate of a parameter. The Fisher matrix in \Eref{eq:fisher-matrix} is block diagonal, which implies that estimation errors in the signal amplitude $\rho$ are uncorrelated with the phase $\gamma$ and time $\tau$. A sequence of two changes of variables lends some physical interpretation to the nature of the coupled estimation errors in $\gamma$ and $\tau$.

>>>>

\DeclareMathOperator{\cov}{cov}
\DeclareMathOperator{\std}{std}

@@

The \ac{CRLB} says that, element by element,
%
\begin{equation}
    \cov{
        \left(
        \begin{array}{c}
            \hat{\rho} - \rho \\
            \hat{\gamma} - \gamma \\
            \hat{\tau} - \tau
        \end{array}
        \right)
    } \geq \mathcal{I}^{-1} = \left(
        \begin{array}{ccc}
            1 & 0 & 0 \\
            0 & \rho^2 \overline{\omega^2}/{\omega_\mathrm{rms}}^2 & \rho^2 \overline{\omega}/{\omega_\mathrm{rms}}^2 \\
            0 & \rho^2 \overline{\omega}/{\omega_\mathrm{rms}}^2 & \rho^2/{\omega_\mathrm{rms}}^2
        \end{array}
    \right)
\end{equation}
%
where a hat $\hat{\phantom{\rho}}$ denotes the estimate of a parameter and ${\omega_\mathrm{rms}}^2 = \overline{\omega^2} - \overline{\omega}^2$. Reading off the $\tau \tau$ element of the covariance matrix reproduces the timing accuracy in Equation~(24) of \cite{fairhurst:2009},
%
\begin{equation}\label{eq:timing-crlb}
    \std \left(\hat{\tau} - \tau \right) \geq \sqrt{\left(\mathcal{I}^{-1}\right)_{\tau\tau}} = \frac{\rho}{\omega_\mathrm{rms}}.
\end{equation}

Furthermore, the Fisher matrix in \Eref{eq:fisher-matrix} is block diagonal, which implies that estimation errors in the signal amplitude $\rho$ are uncorrelated with the phase $\gamma$ and time $\tau$. A sequence of two changes of variables lends some physical interpretation to the nature of the coupled estimation errors in $\gamma$ and $\tau$.
